Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Respond to reviewer wrt table comment.

We have run this set of motion planning problems 20 times. The results are compiled in Table~\ref{table:reaching}.
\begin{table}
\begin{tabular}{lrrrr}
& min & max & average & average \\ 
&&&& per problem \\
number of nodes & 43.00 & 481.00 & 102.70 \\
goal generation time \hspace {1.cm} & 1.00 & 1.56 & 1.22\\
planning time& 67.36 & 376.84 & 134.28 & 44.76\\
\end{tabular}
\caption {Experimental results on 20 runs: 3 motion planning problems and 2 goal generations. Time is expressed in seconds.}
\label{table:reaching}
\end{table}

>>>>

We have run this set of motion planning problems 20 times. The results are compiled in Table~\ref{table:reaching}.
\begin{table}
\begin{tabular}{l|r|r|r|r|}
\cline{2-5}
& min & max & average & average \\ 
&&&& per problem \\
\hline
\multicolumn{1}{|l|}{number of nodes} & 43.00 & 481.00 & 102.70 \\
\cline{1-4}
\multicolumn{1}{|l|}{goal generation time (s)} & 1.00 & 1.56 & 1.22\\
\hline
\multicolumn{1}{|l|}{planning time (s)} & 67.36 & 376.84 & 134.28 & 44.76\\
\hline
\end{tabular}
\caption {\textbf{Experimental results on 20 runs: Each run consists
    of 3 motion planning problems and 2 goal generations for the three
    phases. Time is expressed in seconds.}}
\label{table:reaching}
\end{table}
